SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-03-20 docs/computEL/intro.tex
modified discussion of clustering in intro

We believe the resulting corpus, which at present covers 1347 languages from 106 language families, is the first of its kind: large enough and consistent enough to allow broadly multilingual language processing. Following this claim, we use SeedLing in a test application (\ref{sec:cluster}): the task of language clustering. With no additional pre-processing required, we extract surface-level features (frequencies of character n-grams and words) for estimating the similarity of two languages. Unlike most previous approaches to the task, we make no use of resources curated for aims of linguistic typology (e.g. values of typological features as in WALS \cite{wals}, Swadesh word lists).
\textcolor{blue}{[START HERE WITH CLEARER DESCRIPTION OF CLUSTERING RESULTS]}
Despite this approach being highly dependent on orthography, we are able to reconstruct substantial parts of several language families, demonstrating the utility of this resource in cross-linguistic research. Finally, we discuss future work in section \ref{sec:future}, and conclude in section \ref{sec:conclusion}.

>>>>

We believe the resulting corpus, which at present covers 1347 languages from 106 language families, is the first of its kind: large enough and consistent enough to allow broadly multilingual language processing. Following this claim, we use SeedLing in a test application (\ref{sec:cluster}): the task of language clustering. With no additional pre-processing required, we extract surface-level features (frequencies of character n-grams and words) for estimating the similarity of two languages. Unlike most previous approaches to the task, we make no use of resources curated for aims of linguistic typology (e.g. values of typological features as in WALS \cite{wals}, Swadesh word lists). Despite our approach being highly dependent on orthography, we achieve a reasonable clustering performance over the languages in our dataset, demonstrating SeedLing's utility in cross-linguistic research.

% \textcolor{blue}{[START HERE WITH CLEARER DESCRIPTION OF CLUSTERING RESULTS]}
% Despite this approach being highly dependent on orthography, we are able to reconstruct substantial parts of several language families, demonstrating the utility of this resource in cross-linguistic research. Finally, we discuss future work in section \ref{sec:future}, and conclude in section \ref{sec:conclusion}.

### 2014-03-20 docs/computEL/paper.tex
modified discussion of clustering in intro

\begin{document}
\maketitle
\begin{abstract}
\textcolor{blue}{[revisit abstract]}
The study of endangered languages is constrained by a lack of data. Existing corpora collections are limited in the range of languages covered, in standardisation, or in machine-readability. This makes the situation even worse for the computational linguist, especially one who would like to take a cross-linguistic or typological approach. We first survey existing efforts to compile cross-linguistic resources, then describe our own approach and give an example application - language clustering. To build the foundation text for a Universal Corpus, we crawled and cleaned texts from several web sources that contain data from a large number languages, and converted them into a standardised form consistent with the guidelines set out by \newcite{abney2010universal}. The resulting corpus is more easily-accessible and machine-readable than any of the underlying data sources, and represents a significant base corpus for researchers to draw on and add to in the future.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
\textcolor{blue}{[revisit abstract]}
Computational study of endangered languages is constrained by the lack of digitally-available data. Existing corpora are limited in the range of languages covered, in standardisation, or in machine-readability.
This makes the situation even worse for the computational linguist, especially one who would like to take a cross-linguistic or typological approach. We first survey existing efforts to compile cross-linguistic resources, then describe our own approach and give an example application - language clustering. To build the foundation text for a Universal Corpus, we crawled and cleaned texts from several web sources that contain data from a large number languages, and converted them into a standardised form consistent with the guidelines set out by \newcite{abney2010universal}. The resulting corpus is more easily-accessible and machine-readable than any of the underlying data sources, and represents a significant base corpus for researchers to draw on and add to in the future.
\end{abstract}
